---
title: "Examining the Relationship Between Test Scaled Score and Vertical Scaled Score"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
runtime: shiny
---

```{r setup, include = FALSE}
# global options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# load necessary packages
library(tidyverse)
library(fuzzyjoin)
library(kableExtra)
library(shiny)
library(shinyWidgets)

# load data and transform
extract <- read_csv(
    file = "data/extract_sp2021.csv",
    show_col_types = FALSE
) %>%
    select(
        TestName = `Test Name`, 
        TestScaledScore = `Test Scaled Score`,
        VerticalScaledScore = `Vertical Scale`
    ) %>%
    mutate(
        TestScaledScore = as.numeric(TestScaledScore)
    ) %>%
    na.omit() %>%
    split(.$TestName)

progress <- read_csv(
    file = "data/progress_tables.csv",
    show_col_types = FALSE
)
```

```{r functions, include = FALSE}
# function to produce data frame of summary values
test_summary <- function(.data) {
    return(
        data.frame(
            "Metric" = c("N", "Minimum", "Maximum", "Average"),
            "TestScaledScore" = c(
                nrow(.data),
                round(min(.data$TestScaledScore), 0),
                round(max(.data$TestScaledScore), 0),
                round(mean(.data$TestScaledScore), 0)
            ),
            "VerticalScaledScore" = c(
                nrow(.data),
                round(min(.data$VerticalScaledScore), 0),
                round(max(.data$VerticalScaledScore), 0),
                round(mean(.data$VerticalScaledScore), 0)
            )
        )
    )
}

# function to produce density plots
gg_density <- function(.data, .subtitle) {
    df <- .data %>%
        pivot_longer(
            cols = -TestName,
            names_to = "ScoreType",
            values_to = "Score"
        )
    
    df %>% 
        ggplot(
            mapping = aes(
                x = Score, 
                color = ScoreType, 
                fill = ScoreType, 
                alpha = 0.7
            )
        ) + 
        geom_density() + 
        facet_wrap(
            ~ ScoreType, 
            scales = "free_x"
        ) + 
        theme(legend.position = "none") +
        labs(
            title = "Distribution of Test Scaled Score and Vertical Scaled Score",
            subtitle = .subtitle,
            x = "Score",
            y = "Density"
        )
}

# function to produce scatter plots with line of best fit
gg_scatter <- function(.data, .subtitle) {
    .data %>%
        ggplot(
            mapping = aes(
                x = TestScaledScore,
                y = VerticalScaledScore
            )
        ) +
        geom_point(alpha = 0.7) +
        geom_smooth(
            method = lm, 
            se = FALSE
        ) +
        scale_x_continuous(
            breaks = seq(
                from = 250,
                to = 600,
                by = 50
            ),
            labels = seq(
                from = 250,
                to = 600,
                by = 50
            )
        ) +
        labs(
            title = "Comparison of Test Scaled Score and Vertical Scaled Score",
            subtitle = .subtitle,
            x = "Test Scaled Score",
            y = "Vertical Scaled Score"
        )
}

```

# Introduction

This report details the steps taken to analyze the relationship between a student's test scaled score and vertical scaled score on Virginia Assessment Program (VAP) assessments. The data used to conduct this analysis is the most recent Standards of Learning (SOL) test data for reading and mathematics in grades 3 through 8 from the Spring 2021 administration. No identifying information is kept in the raw data to preserve student anonymity and privacy.

# TL;DR

You can use the dropdown menu to select a test, then enter a score and press submit to convert from test scaled score to vertical scaled score or vice versa.

```{r tldr, echo = FALSE, cache = FALSE}
# get list of test names for dropdown menu
tests <- names(extract)[-1]

# dynamically generate the converted score
output <- eventReactive(input$convert, {
    input_score <- isolate(as.numeric(input$score))
    output_score <- switch(
        input$test,
        "Gr 3 Math CAT" = g3_math_convert(input_score),
        "Gr 3 Reading CAT" = g3_reading_convert(input_score),
        "Gr 4 Math CAT" = g4_math_convert(input_score),
        "Gr 4 Reading CAT" = g4_reading_convert(input_score),
        "Gr 5 Math CAT" = g5_math_convert(input_score),
        "Gr 5 Reading CAT" = g5_reading_convert(input_score),
        "Gr 6 Math CAT" = g6_math_convert(input_score),
        "Gr 6 Reading CAT" = g6_reading_convert(input_score),
        "Gr 7 Math CAT" = g7_math_convert(input_score),
        "Gr 7 Reading CAT" = g7_reading_convert(input_score),
        "Gr 8 Math (16) CAT" = g8_math_convert(input_score),
        "Gr 8 Read (17) CAT" = g8_reading_convert(input_score),
    )
    
    if (input_score <= 600) {
        return(
            div(style = "padding-top: 0.75em; padding-bottom: 0.75em",
                h4(
                    HTML(
                        paste0(
                            "You entered <strong><span style=\"color: green\">",
                            input_score, "</span></strong>, which 
                            is a <strong><em>TEST SCALED SCORE</em></strong>. 
                            </br>
                            </br>
                            The corresponding <strong><em>VERTICAL SCALED SCORE
                            </em></strong> is <strong><span style=\"color: green\">", 
                            output_score, "</span></strong>."
                        )
                    )
                )
            )
        )
    } else {
        return(
            div(style = "padding-top: 0.75em; padding-bottom: 0.75em",
                h4(
                    HTML(
                        paste0(
                            "You entered <strong><span style=\"color: green\">",
                            input_score, "</span></strong>, which 
                            is a <strong><em>VERTICAL SCALED SCORE</em></strong>. 
                            </br>
                            </br>
                            The corresponding <strong><em>TEST SCALED SCORE</em>
                            </strong> is <strong><span style=\"color: green\">", 
                            output_score, "</span></strong>."
                        )
                    )
                )
            )
        )
    }
})

fluidRow(
    column(
        width = 6,
        # create a dropdown menu for the test
        selectInput(
            inputId = "test",
            label = "Choose a test",
            choices = tests
        ),
        
        # create a text input for the score
        textInput(
            inputId = "score",
            label = "Enter a score",
            value = "",
            placeholder = "Test Scaled Score or Vertical Scaled Score"
        ),
        
        # create a button to run the score conversion
        actionButton(
            inputId = "convert",
            label = "Convert Score",
            class = "btn-primary"
        )
    ),
    column(
        width = 6,
        # render the output with the converted score
        renderUI({
            panel(
                output(),
                status = "primary"
            )
        })
    )
)
```

# Reading Assessments

We will begin the analysis with a look at the reading scores for each content tested.

## 3rd Grade Reading

For the 3rd grade reading assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g3_reading, echo = FALSE}
# generate test summary
g3_reading <- test_summary(extract$`Gr 3 Reading CAT`)

# display the summary as a table
g3_reading %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 3 Reading CAT` %>%
    gg_density("Grade 3 Reading")

# generate linear model
g3_reading_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 3 Reading CAT`)

# build third grade reading conversion function
g3_reading_convert <- function(.score) {
    intercept <- g3_reading_lm$coefficients[[1]]
    slope = g3_reading_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g3_reading_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 3 Reading CAT` %>%
    gg_scatter("Grade 3 Reading")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 3 Reading is perfectly linear. The relationship is modeled as:

\[
V = 632.9793 + 2.052755T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

## 4th Grade Reading

For the 4th grade reading assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g4_reading, echo = FALSE}
# generate test summary
g4_reading <- test_summary(extract$`Gr 4 Reading CAT`)

# display the summary as a table
g4_reading %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 4 Reading CAT` %>%
    gg_density("Grade 4 Reading")

# generate linear model
g4_reading_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 4 Reading CAT`)

# build third grade reading conversion function
g4_reading_convert <- function(.score) {
    intercept <- g4_reading_lm$coefficients[[1]]
    slope = g4_reading_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g4_reading_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 4 Reading CAT` %>%
    gg_scatter("Grade 4 Reading")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 4 Reading is perfectly linear. The relationship is modeled as:

\[
V = 733.04 + 1.91T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

## 5th Grade Reading

For the 5th grade reading assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g5_reading, echo = FALSE}
# generate test summary
g5_reading <- test_summary(extract$`Gr 5 Reading CAT`)

# display the summary as a table
g5_reading %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 5 Reading CAT` %>%
    gg_density("Grade 5 Reading")

# generate linear model
g5_reading_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 5 Reading CAT`)

# build third grade reading conversion function
g5_reading_convert <- function(.score) {
    intercept <- g5_reading_lm$coefficients[[1]]
    slope = g5_reading_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g5_reading_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 5 Reading CAT` %>%
    gg_scatter("Grade 5 Reading")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 5 Reading is perfectly linear. The relationship is modeled as:

\[
V = 724.44 + 2.05T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

## 6th Grade Reading

For the 6th grade reading assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g6_reading, echo = FALSE}
# generate test summary
g6_reading <- test_summary(extract$`Gr 6 Reading CAT`)

# display the summary as a table
g6_reading %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 6 Reading CAT` %>%
    gg_density("Grade 6 Reading")

# generate linear model
g6_reading_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 6 Reading CAT`)

# build third grade reading conversion function
g6_reading_convert <- function(.score) {
    intercept <- g6_reading_lm$coefficients[[1]]
    slope = g6_reading_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g6_reading_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 6 Reading CAT` %>%
    gg_scatter("Grade 6 Reading")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 6 Reading is perfectly linear. The relationship is modeled as:

\[
V = 822.10 + 1.88T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

## 7th Grade Reading

For the 7th grade reading assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g7_reading, echo = FALSE}
# generate test summary
g7_reading <- test_summary(extract$`Gr 7 Reading CAT`)

# display the summary as a table
g7_reading %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 7 Reading CAT` %>%
    gg_density("Grade 7 Reading")

# generate linear model
g7_reading_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 7 Reading CAT`)

# build third grade reading conversion function
g7_reading_convert <- function(.score) {
    intercept <- g7_reading_lm$coefficients[[1]]
    slope = g7_reading_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g7_reading_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 7 Reading CAT` %>%
    gg_scatter("Grade 7 Reading")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 7 Reading is perfectly linear. The relationship is modeled as:

\[
V = 852.53 + 1.89T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

## 8th Grade Reading

For the 8th grade reading assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g8_reading, echo = FALSE}
# generate test summary
g8_reading <- test_summary(extract$`Gr 8 Read (17) CAT`)

# display the summary as a table
g8_reading %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 8 Read (17) CAT` %>%
    gg_density("Grade 8 Reading")

# generate linear model
g8_reading_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 8 Read (17) CAT`)

# build third grade reading conversion function
g8_reading_convert <- function(.score) {
    intercept <- g8_reading_lm$coefficients[[1]]
    slope = g8_reading_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g8_reading_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 8 Read (17) CAT` %>%
    gg_scatter("Grade 8 Reading")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 8 Reading is perfectly linear. The relationship is modeled as:

\[
V = 872.81 + 1.88T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

<!-- # Reading Assessment Overlap -->

<!-- As a final component of the reading score analysis, we look at the overlap of the vertical scaled score ranges as a function of the test scaled score to understand the relationship between grade levels. -->

<!-- ```{r reading_comp} -->

<!-- reading_df <- data.frame( -->
<!--     TestScaledScore = seq( -->
<!--         from = 0, -->
<!--         to = 600, -->
<!--         by = 1 -->
<!--     ) -->
<!-- ) %>% -->
<!--     mutate( -->
<!--         Reading3 = g3_reading_convert(TestScaledScore), -->
<!--         Reading4 = g4_reading_convert(TestScaledScore), -->
<!--         Reading5 = g5_reading_convert(TestScaledScore), -->
<!--         Reading6 = g6_reading_convert(TestScaledScore), -->
<!--         Reading7 = g7_reading_convert(TestScaledScore), -->
<!--         Reading8 = g8_reading_convert(TestScaledScore) -->
<!--     ) %>% -->
<!--     pivot_longer( -->
<!--         cols = -TestScaledScore, -->
<!--         names_to = "Test", -->
<!--         values_to = "VerticalScaledScore" -->
<!--     ) %>% -->
<!--     filter( -->
<!--         between( -->
<!--             x = VerticalScaledScore, -->
<!--             left = 900, -->
<!--             right = 2000 -->
<!--         ) -->
<!--     ) %>% -->
<!--     fuzzy_inner_join( -->
<!--         y = progress, -->
<!--         by = list( -->
<!--             x = c( -->
<!--                 "Test", -->
<!--                 "VerticalScaledScore", -->
<!--                 "VerticalScaledScore" -->
<!--             ), -->
<!--             y = c( -->
<!--                 "Test", -->
<!--                 "MinScore", -->
<!--                 "MaxScore" -->
<!--             ) -->
<!--         ), -->
<!--         match_fun = list(`==`, `>=`, `<=`) -->
<!--     ) %>% -->
<!--     select( -->
<!--         "Test" = Test.x, -->
<!--         TestScaledScore, -->
<!--         VerticalScaledScore, -->
<!--         Range -->
<!--     ) %>% -->
<!--     mutate( -->
<!--         Test = as.factor(Test), -->
<!--         Range = as.factor(Range) -->
<!--     ) -->

<!-- reading_df %>% -->
<!--     ggplot( -->
<!--         mapping = aes( -->
<!--             x = Test, -->
<!--             y = VerticalScaledScore, -->
<!--             color = Range -->
<!--         ) -->
<!--     ) + -->
<!--     geom_col() + -->
<!--     coord_flip() -->
<!--     #geom_jitter(position = position_jitter(0.2)) -->
<!-- ``` -->

# Math Assessments

We complete the analysis with a look at the math scores for each content tested.

## 3rd Grade Math

For the 3rd grade math assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g3_math, echo = FALSE}
# generate test summary
g3_math <- test_summary(extract$`Gr 3 Math CAT`)

# display the summary as a table
g3_math %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 3 Math CAT` %>%
    gg_density("Grade 3 Math")

# generate linear model
g3_math_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 3 Math CAT`)

# build third grade reading conversion function
g3_math_convert <- function(.score) {
    intercept <- g3_math_lm$coefficients[[1]]
    slope = g3_math_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g3_math_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 3 Math CAT` %>%
    gg_scatter("Grade 3 Math")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 3 Math is perfectly linear. The relationship is modeled as:

\[
V = 759.7 + 1.6T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

## 4th Grade Math

For the 4th grade math assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g4_math, echo = FALSE}
# generate test summary
g4_math <- test_summary(extract$`Gr 4 Math CAT`)

# display the summary as a table
g4_math %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 4 Math CAT` %>%
    gg_density("Grade 4 Math")

# generate linear model
g4_math_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 4 Math CAT`)

# build third grade reading conversion function
g4_math_convert <- function(.score) {
    intercept <- g4_math_lm$coefficients[[1]]
    slope = g4_math_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g4_math_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 4 Math CAT` %>%
    gg_scatter("Grade 4 Math")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 4 Math is perfectly linear. The relationship is modeled as:

\[
V = 777.82 + 1.63T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

## 5th Grade Math

For the 5th grade math assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g5_math, echo = FALSE}
# generate test summary
g5_math <- test_summary(extract$`Gr 5 Math CAT`)

# display the summary as a table
g5_math %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 5 Math CAT` %>%
    gg_density("Grade 5 Math")

# generate linear model
g5_math_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 5 Math CAT`)

# build third grade reading conversion function
g5_math_convert <- function(.score) {
    intercept <- g5_math_lm$coefficients[[1]]
    slope = g5_math_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g5_math_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 5 Math CAT` %>%
    gg_scatter("Grade 5 Math")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 5 Math is perfectly linear. The relationship is modeled as:

\[
V = 851.25 + 1.61T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

## 6th Grade Math

For the 6th grade math assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g6_math, echo = FALSE}
# generate test summary
g6_math <- test_summary(extract$`Gr 6 Math CAT`)

# display the summary as a table
g6_math %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 6 Math CAT` %>%
    gg_density("Grade 6 Math")

# generate linear model
g6_math_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 6 Math CAT`)

# build third grade reading conversion function
g6_math_convert <- function(.score) {
    intercept <- g6_math_lm$coefficients[[1]]
    slope = g6_math_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g6_math_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 6 Math CAT` %>%
    gg_scatter("Grade 6 Math")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 6 Math is perfectly linear. The relationship is modeled as:

\[
V = 888.04 + 1.61T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

## 7th Grade Math

For the 7th grade math assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g7_math, echo = FALSE}
# generate test summary
g7_math <- test_summary(extract$`Gr 7 Math CAT`)

# display the summary as a table
g7_math %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 7 Math CAT` %>%
    gg_density("Grade 7 Math")

# generate linear model
g7_math_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 7 Math CAT`)

# build third grade reading conversion function
g7_math_convert <- function(.score) {
    intercept <- g7_math_lm$coefficients[[1]]
    slope = g7_math_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g7_math_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 7 Math CAT` %>%
    gg_scatter("Grade 7 Math")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 7 Math is perfectly linear. The relationship is modeled as:

\[
V = 956.51 + 1.56T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.

## 8th Grade Math

For the 8th grade math assessment given during the Spring 2021 administration, students were assigned both a test scaled score and vertical scaled score. A summary of the scores, as well as density plots, are shown below.

```{r g8_math, echo = FALSE}
# generate test summary
g8_math <- test_summary(extract$`Gr 8 Math (16) CAT`)

# display the summary as a table
g8_math %>%
    kbl() %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed", "responsive")
    )

# produce the density plots
extract$`Gr 8 Math (16) CAT` %>%
    gg_density("Grade 8 Math")

# generate linear model
g8_math_lm <- lm(VerticalScaledScore ~ TestScaledScore, data = extract$`Gr 8 Math (16) CAT`)

# build third grade reading conversion function
g8_math_convert <- function(.score) {
    intercept <- g8_math_lm$coefficients[[1]]
    slope = g8_math_lm$coefficients[[2]]
    
    converted <- if_else(
        condition = .score <= 600,
        true = slope * .score + intercept,
        false = (.score - intercept) / slope
    )
    
    return(round(converted))
}
```

\vspace{\baselineskip}

We can also produce a scatter plot and the accompanying line of best fit.

```{r g8_math_fit, echo = FALSE}
# produce the scatter plot with line of best fit
extract$`Gr 8 Math (16) CAT` %>%
    gg_scatter("Grade 8 Math")
```

\vspace{\baselineskip}

As we can see from the scatter plot and line of best fit, the relationship between test scaled score and vertical scaled score for Grade 8 Math is perfectly linear. The relationship is modeled as:

\[
V = 940.52 + 1.67T
\]

where $V$ is the vertical scaled score and $T$ is the test scaled score.
